---
title: "RapTLR Training Guide"
subtitle: "Rapid Top-Line Report Generation with R"
author: "RapTLR Development Team"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
description: "Complete training material for the RapTLR package"
---

# Introduction {#intro}

## What is RapTLR?

RapTLR (pronounced "raptor") is an R package designed to automate and streamline the creation of Top-Line Reports (TLRs) in clinical trials. It eliminates manual, error-prone tasks by:

- **Automatically appending TLFs** (Tables, Listings, Figures) to Word documents with hyperlinks
- **Dynamically replacing placeholder text** with calculated values from your data
- **Creating formatted text descriptions** of variable distributions

## Why Use RapTLR?

Traditional TLR creation involves:

- Manual copy-pasting of outputs into Word documents
- Manually updating numbers when data changes
- Risk of transcription errors
- Time-consuming formatting

**RapTLR solves these problems** by connecting your R analysis directly to your Word document, ensuring accuracy and saving hours of work.

## Installation

```{r eval=FALSE}
# Install remotes if needed
install.packages("remotes")

# Install RapTLR from GitHub
library(remotes)
remotes::install_github("johnsonandjohnson/RapTLR")
```

## Getting Started with Examples

RapTLR includes built-in examples to help you learn quickly:

```{r eval=FALSE}
library(RapTLR)

# Export example files to your working directory
export_examples(path_workingFolder = "C:/Documents/TLR_folder/")
```

This creates two folders:
- `TLF_outputs/` - Contains dummy TLF files (PDFs)
- `TLR_shell/` - Contains a template Word document

## Typical Workflow

```{r eval=FALSE}
# 1. Load your data and create TLFs
# 2. Prepare a Word shell document with placeholders
# 3. Use run_apdx() to add TLFs as appendices
# 4. Use textReplace() to update placeholder text
# 5. Generate final TLR document
```

## Package Dependencies

RapTLR relies on the `officer` package for Word document manipulation. Key concepts:

- Documents are R objects that can be modified
- Changes can be chained together
- Final output is written to a file

Let's dive into each component!
